\documentclass{mycv}

\name[Srujan]{Srujan Sai Rapolu}
\phone{+91 8074095127}
\email{rsrujansai@gmail.com}
\github{srujaan}


\begin{document}

\maketitle%
\section{Career \\ Objective}
\begin{description}
  \item Hands-on experience in handling and processing ETL application with extensive       
  knowledge of 
  \item testing and data warehouse. Interested in learning new technologies. Looking for a responsible 
  \item position as an ETL tester in an organization.
\end{description}

\section{Education}

\subsection{TKR College of Engineering and Technology}[Hyderabad, TS, India]
\vspace{-\parskip}%
\begin{itemize}[label={}]
  \item Bachelor of Engineering in ECE  \printdate{August 2014~--~July 2018}
  \item Grade: 60.38\%
\end{itemize}
\vspace{-\parskip}%
\subsection{Sri Chaitanya Junior College}[Hyderabad, TS, India]
\vspace{-\parskip}%
\begin{itemize}[label={}]
  \item Board of Intermediate Education \printdate{May 2012~--~June 2014}
  \item Grade: 83\%
\end{itemize}
\vspace{-\parskip}%
\subsection{Sri Krishnaveni Talent School}[Nagarkurnool, TS, India]
\vspace{-\parskip}%
\begin{itemize}[label={}]
  \item Secondary School Certificate \printdate{April 2011~--~April 2012}
  \item Grade: 9.0 GPA
\end{itemize}
\section{Technical \\ Skills}

\begin{description}
  \item[ETL Tools] Informatica IDQ 10.1.1
  \item[Databases] Oracle 11g, MS SQL Server 2017.
  \item[Tools] IBM Netezza, Spring Boot, Microsoft Excel, Git, Eclipse.
  \item[Programming] Python, Java.
  \item[Operating Systems] Windows 10, Windows Server 2012 R2, Linux.
\end{description}


\section{Professional \\ Experience }

\subsection{Tech Mahindra}[Pune, MH, India]
\begin{positions}
  \entry{Software Engineer}{April 2019~--~November 2020}
\end{positions}

\begin{itemize}
  \item Worked as an ETL QA Tester for UK's largest Telecom provider TalkTalk.
  \item Created Netezza SQL scripts to test the table loaded correctly.
  \item Analyzed and understood the ETL work flows developed.
  \item Performed Data Analysis and improved Data Mapping.
  \item Involved in Unit testing and Integration testing of mappings and workflows.
  \item Modified and improved IDQ mappings for PII columns.
  \item Developed Test Cases and SQL Queries to perform various Validations.
  \item Involved in Troubleshooting, resolving and escalating data related issues and validating data to improve data quality.
  \item A very good team player with excellent Communication and reporting skills.
  \item Familiar with Java and its micro services .
  
\end{itemize}

\section{Responsibilities}

\begin{itemize}
  \item Validating the data files from source to make sure correct data has been captured to be loaded to target tables.
   \item Raising defects where discrepancy found in the database and reporting it to the onshore development team.
   \item Attended daily Scrum calls with internal team and weekly calls with client  and updated the status report.
   

\end{itemize}

\section{Academic \\ Project}
\subsection{Real-Time Mobile Robot using Computer Vision Libraries}
\vspace{-\parskip}%
\begin{itemize}
	\item Designed and implemented a manually controlled mobile robot using Raspberry Pi.
	\item Integrated OCR computer vision library for conversion of printed text into machine-encoded text and display the directions on a screen.
	\item Piloted the robot in the desired direction with appropriate text and achieved 80\% accuracy rate.
\end{itemize}


\section{Certifications}
\vspace{-\parskip}%
\begin{itemize}
	\item Full Stack Developer - Java Stack \hspace{5.5cm} TalentSprint BootCamp
\item Programming for Everybody (Getting Started with Python).\hspace{3.9cm}Coursera
	\item Neural Networks and Deep Learning. \hspace{7.1cm}Coursera
\end{itemize} 
\end{document}

